Improving inference of evolutionary history

### 2014-11-03 slides/osu/slides.tex
More work on slides for osu.

{
\usebackgroundtemplate{\includegraphics[width=\paperwidth]{../images/maps/se-asia-present.png}}
\begin{frame}
    \frametitle{Southeast Asia}    
\end{frame}
}

{
\usebackgroundtemplate{\includegraphics[width=\paperwidth]{../images/maps/se-asia-120.png}}
\begin{frame}
    \frametitle{Southeast Asia}    
    \begin{columns}
        \column{0.6\textwidth}
        \ \\

@@

        \begin{uncoverenv}<2->
        \colorbox{white}{
            \begin{minipage}[t][3.6cm][t]{1.1\textwidth}
                \begin{onlyenv}<2-3>
                \begin{itemize}
                    \item<2-> Repeated coalescence and fragmentation of island complexes
                    \item<3-> Prominent paradigm for explaining biodiversity
                \end{itemize}
                \end{onlyenv}

                \begin{onlyenv}<4>
                \begin{itemize}
                    \item<4> \textbf{Did repeated fragmentation of islands
                        during inter-glacial rises in sea level promote
                        diversification?}
                \end{itemize}
                \end{onlyenv}

                \begin{onlyenv}<5->
                \begin{itemize}
                    \item<5-> Climate-driven model of diversification
                    \item<6-> Testable prediction:
                    \begin{itemize}
                        \item Temporally clustered divergences among taxa
                            co-distributed across fragmented islands
                    \end{itemize}
                \end{itemize}
                \end{onlyenv}
            \end{minipage}
        }
    \end{uncoverenv}
    \end{columns}
\end{frame}
}

@@

    \frametitle<1-4>{Community scale processes}

@@

    \vspace{-1mm}
    \begin{center}
        % \includegraphics<1>[height=7.8cm]{../images/marginal-plot-2d-uniform-prior.pdf}
        \includegraphics<2>[height=7.8cm]{../images/marginal-plot-3d.png}
        \includegraphics<3>[height=7.8cm]{../images/marginal-plot-2d-uniform-prior.pdf}
        \includegraphics<4>[height=7.8cm]{../images/marginal-plot-2d.pdf}
    \end{center}
\end{frame}

>>>>

{
\usebackgroundtemplate{\includegraphics[width=\paperwidth]{../images/maps/se-asia-present.png}}
\begin{frame}
    \frametitle{Climate-driven diversification}    
\end{frame}
}

@@

        \begin{uncoverenv}<2->
        \colorbox{white}{
            \begin{minipage}[t][3.6cm][t]{1.1\textwidth}
                % \begin{onlyenv}<2-3>
                % \begin{itemize}
                %     \item<2-> Repeated coalescence and fragmentation of island complexes
                %     \item<3-> Prominent paradigm for explaining biodiversity
                % \end{itemize}
                % \end{onlyenv}

                \begin{onlyenv}<2>
                \begin{itemize}
                    \item \textbf{Did repeated fragmentation of islands
                        during inter-glacial rises in sea level promote
                        diversification?}
                \end{itemize}
                \end{onlyenv}

                \begin{onlyenv}<3->
                \begin{itemize}
                    \item<3-> Climate-driven model of diversification
                    \item<4-> Testable prediction:
                    \begin{itemize}
                        \item Temporally clustered divergences among taxa
                            co-distributed across fragmented islands
                    \end{itemize}
                \end{itemize}
                \end{onlyenv}
            \end{minipage}
        }
    \end{uncoverenv}
    \end{columns}
\end{frame}
}

@@

    \frametitle<1-4>{Climate-driven model: Predictions}

@@

    \vspace{-1mm}
    \begin{center}
        % \includegraphics<1>[height=7.8cm]{../images/marginal-plot-2d-uniform-prior.pdf}
        \includegraphics<2>[height=7.8cm]{../images/marginal-plot-3d-bare.png}
        \includegraphics<3>[height=7.8cm]{../images/marginal-plot-3d-constrained.png}
        \includegraphics<4>[height=7.8cm]{../images/marginal-plot-3d.png}
        \includegraphics<5>[height=7.8cm]{../images/marginal-plot-2d-uniform-prior.pdf}
        \includegraphics<6>[height=7.8cm]{../images/marginal-plot-2d.pdf}
    \end{center}
\end{frame}
